Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-09 paper/BayesianLISTA.tex
experiment results processing

\subsection{MNIST}
Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun2010mnist}. The dataset contains images of handwritten digits of size $28 \times 28 = 784$. The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm \citep{mairal2009online}. The resulting size of $\mathbf{X}$ is $100 \times 784$. Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta$ are images converted to vectors. We use randomly selected 1000 images for training and 100 for validation.

Figure \ref{fig:validation} presents \textsc{nmse} loss on the validation set.

Proposed Bayesian \textsc{lista} networks estimate posterior distribution for $\boldsymbol\beta$. Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and figure \ref{fig:posterior_distribution} shows the parameters of this posterior.
\begin{figure}[t]
\includegraphics[width=\columnwidth]{loss}
\caption{Validation \textsc{nmse}}
\label{fig:validation}
\end{figure}
\begin{figure*}[t]
\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.66\columnwidth]{posterior_mean}}
\subfloat[$\beta$ posterior std]{\includegraphics[width=0.66\columnwidth]{posterior_std}}
\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.66\columnwidth]{posterior_spike_indicator}}
\caption{Posterior for the digit 7.}
\label{fig:posterior_distribution}
\end{figure*}
\begin{figure*}[t]
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_0}}
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_1}}
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_2}}
\caption{Samples from the posterior for the digit 7.}
\label{fig:posterior_samples}
\end{figure*}

>>>>

\subsection{Predictive performance on synthetic data}
Here we evaluate the proposed Bayesian \textsc{lista} in terms of predictive performance on the \textsc{mnist} dataset \citep{lecun2010mnist}. The dataset contains images of handwritten digits of size $28 \times 28 = 784$. The design matrix $\mathbf{X}$ is learned on 5000 images with the minibatch online algorithm \citep{mairal2009online}. The resulting size of $\mathbf{X}$ is $K \times 784$. Then we generate observations as $\mathbf{y} = \mathbf{X}\boldsymbol\beta$, where $\boldsymbol\beta$ are images converted to vectors. We use randomly selected $100$ images for training and $100$ for validation.

Figures \ref{fig:mnist_100}, \ref{fig:mnist_250} presents \textsc{nmse} loss on the validation set with dictionaries $100$ and $250$.

Proposed Bayesian \textsc{lista} networks estimate posterior distribution for $\boldsymbol\beta$. Figure \ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and figure \ref{fig:posterior_distribution} shows the parameters of this posterior.

\begin{figure}[t]
\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
\newline
\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
\caption{\textsc{mnist} with dictionary $100$}
\label{fig:mnist_100}
\end{figure}

\begin{figure}[t]
\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_train}}
~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_nmse_valid}}
\newline
\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_train}}
~
\subfloat[F measure on validation]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/250_normalised_f_measure_valid}}
\caption{\textsc{mnist} with dictionary $250$}
\label{fig:mnist_250}
\end{figure}

%\begin{figure}[t]
%\includegraphics[width=\columnwidth]{loss}
%\caption{Validation \textsc{nmse}}
%\label{fig:validation}
%\end{figure}
\begin{figure*}[t]
\subfloat[$\beta$ posterior mean]{\includegraphics[width=0.66\columnwidth]{posterior_mean}}
\subfloat[$\beta$ posterior std]{\includegraphics[width=0.66\columnwidth]{posterior_std}}
\subfloat[$\beta$ posterior spike indicator]{\includegraphics[width=0.66\columnwidth]{posterior_spike_indicator}}
\caption{Posterior for the digit 7.}
\label{fig:posterior_distribution}
\end{figure*}
\begin{figure*}[t]
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_0}}
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_1}}
\subfloat[]{\includegraphics[width=0.66\columnwidth]{posterior_sample_2}}
\caption{Samples from the posterior for the digit 7.}
\label{fig:posterior_samples}
\end{figure*}
